---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(collapse=TRUE, comment="##", fig.retina=2, fig.path = "README_figs/README-")
library(tidyverse)
```

## `ggwehi`:  Colour scales for `ggplot2` based on the WEHI colour palette

### Installation
```{r, eval=FALSE}
devtools::install_github("jemunro/ggwehi")
```

### Examples
```{r examples}
library(tidyverse)
library(ggwehi)

diamonds %>% 
  ggplot(aes(x = cut, fill = clarity)) +
  geom_bar() +
  scale_fill_wehi() +
  ggtitle('scale_fill_wehi()')
set.seed(1)
tibble(state = c(rbind(str_c(1:5, 'A'), str_c(1:5, 'B'))),
       class = str_extract(state, '^.'),
       condition = str_extract(state, '.$'),
       value = abs(rnorm(length(class)))) %>% 
  ggplot(aes(class, value, fill = state)) +
  geom_col() +
  scale_fill_wehi_paired() +
  ggtitle('scale_fill_wehi_paired()')
set.seed(2)
diamonds %>% 
  sample_n(5000) %>%
  ggplot(aes(x = cut, y = carat, col = price)) +
  geom_jitter(height = 0, width = 0.35) + 
  geom_boxplot(fill = NA, outlier.colour = NA, col = 'black') +
  scale_colour_wehi_continuous() +
  ggtitle('scale_colour_wehi_continuous()')
```

### Scale functions
* `scale_fill_wehi()`/`scale_colour_wehi()`
  * Supports up to 8 different colours
  * Note: `na.value` is set to `ggwehi::wehi_grey` (grey from wehi_primary)
* `scale_fill_wehi_paired()`/`scale_colour_wehi_paired()`
  * Supports up to 8 pairs, with 16 different colours
  * Note: This will only work if the aesthetic is such that when alphabetically sorted the pairs are adjacent to one another, and all pairs are complete. For a more general solution use `scale_fill_manual(values = x)` where x is a named vector of values from ggwehi::wehi_paired.
* `scale_fill_wehi_continuous()`/`scale_colour_wehi_continuous()`

### Palettes
```{r palettes}
scales::show_col(wehi_primary)
scales::show_col(wehi_secondary)
scales::show_col(wehi_extended)
scales::show_col(wehi_paired)
scales::show_col(wehi_continous()(seq(0,1,1/15)))
```
